### 2019-03-21 3_task_bench.tex
Fix typo.

In order to measure properties such as METG for a wide variety of
systems and application scenarios, we developed a novel
\emph{parameterized} benchmark called Task Bench. Task Bench
implementations execute a \emph{task graph}, with tasks for each point
in an \emph{iteration space} and dependencies between tasks determined
by a \emph{dependence relation}. Each task can execute any one of a
number of kernels (compute-bound, memory-bound, etc.) and can generate
a configurable amount of result data in order to the amount of
communications that must be performed. Thus Task Bench can be used to
rapidly explore a large space of possible application scenarios in
order to understand the performance behaviors of parallel and
distributed languages and runtime systems.

>>>>

In order to measure properties such as METG for a wide variety of
systems and application scenarios, we developed a novel
\emph{parameterized} benchmark called Task Bench. Task Bench
implementations execute a \emph{task graph}, with tasks for each point
in an \emph{iteration space} and dependencies between tasks determined
by a \emph{dependence relation}. Each task can execute any one of a
number of kernels (compute-bound, memory-bound, etc.) and can generate
a configurable amount of result data in order to control the amount of
communication that must be performed with each task dependency. Thus Task Bench can be used to
rapidly explore a large space of possible application scenarios in
order to understand the performance behaviors of parallel and
distributed languages and runtime systems.
